Recursive Solutions to First-Order Model Counting

### 2022-08-16 doc/talks/workshop_talk/talk.tex
Small changes

\begin{frame}{Back to Our Example}
  For instance, the following function counts injections
  \[
  f(m, n) =
  \begin{cases}
    1 & \text{if } m = 0 \text{ and } n = 0 \\
    0 & \text{if } m > 0 \text{ and } n = 0 \\
    f(m, n-1) + mf(m-1, n-1) & \text{otherwise.}
  \end{cases}
  \]
  \pause
  \begin{itemize}
  \item \structure{$f$} can be computed in \structure{$\Theta(mn)$} time (via dynamic programming).
  \item Optimal time complexity to compute \structure{$n^{\underline{m}}$} is \structure{$\Theta(\log m)$}.
  \item But \structure{$\Theta(mn)$} is still much better than solving an equivalent \alert{$\#\P$-complete} problem in propositional logic.
  \item The rest of this talk is about how such functions can be found automatically.
  \end{itemize}
\end{frame}

>>>>

\begin{frame}{Back to Our Example}
  For instance, the following function counts injections
  \[
  f(m, n) =
  \begin{cases}
    1 & \text{if } m = 0 \text{ and } n = 0 \\
    0 & \text{if } m > 0 \text{ and } n = 0 \\
    f(m, n-1) + mf(m-1, n-1) & \text{otherwise.}
  \end{cases}
  \]
  \pause
  \begin{itemize}
    \item \structure{$f$} can be computed in \structure{$\Theta(mn)$} time (via
          dynamic programming).
    \item Optimal time complexity to compute \structure{$n^{\underline{m}}$} is
          \structure{$\Theta(m)$}.
    \item But \structure{$\Theta(mn)$} is still much better than translating to
          propositional logic and running a WMC algorithm.
    \item The rest of this talk is about how such functions can be found
          automatically.
  \end{itemize}
\end{frame}
